---
title: "What happened to 'the right is coming'?"
output: github_document
---

(Alternative title: "Mr. Sánchez, is the far right coming or not?")

```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 8.64,
               fig.height = 4.86,
               fig.path = 'figures/')
```

```{r}
source('prepare_data.R')
```

# The importance of having an adversary

Though politicians claim that they want to do "positive" campaigns (that is, highlighting the advantages of their own policies without overly criticizing others'), reality clearly shows the opposite. Politicians talk incessantly about other politicians, and they tend to talk more about their adversaries than their allies. Why? Because the strategy pays off: talking about your adversary rallies up the base. They all do it. No politician is capable of resisting the temptation to criticize their adversary, because mere existence of the adversary is too useful of a political concept to pass on.

Given the universality of the strategy, it's difficult to make comparisons between different parties. On the other hand, even though one can't compare the "what" (since the strategy of talking about adversaries is universal), one _can_ compare the "who": which adversary do parties choose to focus on, why, when do they change adversaries, and what is the result that they hope for with the choice of one adversary versus another.


# April 28 elections: the "right" as the adversary

The strategy of the socialist party in the April 28 elections was to frame the right as their adversary. One can quantify this strategy just by looking at the frequency with which Pedro Sánchez, and other socialist leaders, mentioned the "right" during the campaign. The following chart shows the percentage of monthly tweets which contain the words "right" in Catalan or Spanish ("derecha", "derechas", "dreta", o "dretes") from the main Spanish and Catalan politicians, through the end of September 2019.

```{r}
make_pre_election_plot()
```

What stands out most is the sharp increase in the frequency of references to the right in the months leading up to the April 2019 elections. The socialists had previously only referenced the right in less than 1% of tweets. But, beginning at the start of 2019 (with the upcoming elections), this number increased steadily, reaching a peak of over 9% in the month of the elections. The strategy appears to be coordinated, because at the individual level nearly all the socialist politicians increased the frequnecy with which they referenced the right in the months prior to the elections, especially in the month of the elections themselves.

```{r}
make_pre_election_plot_person()
```

# The change of strategy

Did it work? No. The results of the April 28 elections were not satisfactory for the socialist (the proof being that, had they been satisfactory, they would not have called for another round of elections). Despite having won more votes than any other party at the level of the Spanish State, the strategy of using the right as the "adversary" left them in an uncomfortable position: having positioned themselves as the brake on the "trifachito", the only political forces left with which they could form a government were the pro-sovereignty ones, and Sánchez did not want to have a government which depended on people who were in favor of Catalonia's self-determination.

Since positioning themselves as the opposite of the "right" left them without the possibility of forming a government, the socialists decided to change their strategy. Since (i) they did not want to form a government with the pro-sovereignty forces and (ii) it's very unlikely that they would obtain an absolute majority, there's only one other possibility: they plan to make a deal with one of the three parties which they previously referred to as the "trifachito". And if they consider that having to make a deal with the right is inevitable (this is the case), then painting the picture f the right as the "adversary" is no longer such a useful strategy.

With only 6 weeks until the November 10 elections, the change in strategy is clear: they don't talk about the right any more because the right is who they plan to govern with. Let's take a look at the rate of mentions of the right over the last few months:


```{r}
make_post_election_plot()
```

The change in strategy is similarly clear at the individual level. For example, neither Eva Granados, nor Josep Borrell, nor Pedro Sánchez mentioned the right even once on Twitter from May through September. And those who still do reference the right do so at a much lower rate than prior the April 28 elections:


```{r}
make_post_election_plot_person()
```

The strategy of not talking about the right can be observed in the socialist party's official accounts (both Spanish and Catalan), where the percentage of tweets which reference the right has fallen drastically since the elections, and appears not to be increasing, despite the fact that the November 10th elections are only weeks away:


```{r}
make_post_election_plot_party()
```


# Conclusion

Is the right coming or not? Why does Pedro Sánchez no longer talk about "the right and its three initials"?  Why does Miquel Iceta no longer talk about the fear of a "francostein" government? Why have ALL the socialist politicians, both in Catalonia as well as the restr of the Spanish State, stopped referencing the right as their political adversary? Why did they stop talking about the right completely?

The answer is clear: in order to prevent groups which are in favor of self-determination from influencing Spain's government, Sánchez will have to make a deal with the right. And since this option is not popular among his voters, he needs to simply avoid the topic so as to not demotivate them. But carrying out an electoral campaign without an adversary and without saying who you plan to form a government with is very difficult, especially in the case of repeat elections in which the abstention factor will be crucial.

Since they can no longer use the "right" as their adversary (since they will be their future colleagues in government), which adversary can the socialists use to try to motivate people to go vote? If the "fear" that the far right is coming didn't work well enough as a strategy, what other group might produce enough "fear" for people to go vote for Sánchez in November. The last few weeks have made the answer to this question very clear: Catalonia, its "violence", its "terrorists", and its "insurrectional" government.



# Technical details

- The Twitter accounts analyzed were all of the socialist parlementarians in the Catalan Parlament as well as all the Ministers of the Sánchez government with a known Twitter account:

```{r}
x <- socialists %>%
  mutate(full_name = ifelse(is.na(full_name),
                            name,
                            full_name)) %>%
  dplyr::select(full_name, username)
names(x) <- c('Name', 'Twitter')
kable(x)
```

- Tweets through September 30, 2019. 
- All the code for this analysis is publicly available: `r self_cite()`.