---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# vilaweb: The R package of Joe Brew's VilaWeb data analysis

## Installation


```r
if(!require(devtools)) install.packages("devtools")
install_github('joebrew/vilaweb')
```


```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.width = 4,
                      fig.height = 4)
library(dplyr)
library(tidyr)
library(ggplot2)
library(cism)

# knitr::knit_hooks$set(
#    error = function(x, options) {
#      paste('\n\n<div class="alert alert-danger">',
#            gsub('##', '\n', gsub('^##\ Error', '**Error**', x)),
#            '</div>', sep = '\n')
#    },
#    warning = function(x, options) {
#      paste('\n\n<div class="alert alert-warning">',
#            gsub('##', '\n', gsub('^##\ Warning:', '**Warning**', x)),
#            '</div>', sep = '\n')
#    },
#    message = function(x, options) {
#      paste('\n\n<div class="alert alert-info">',
#            gsub('##', '\n', x),
#            '</div>', sep = '\n')
#    }
# )
```

## About

`vilaweb` is...


## Developer details

In order to reproduce the entire package, raw data will need to be downloaded from various sources

### Downloading raw data

#### 1. Download CIS data

Download into `data-raw/cis/fichero_integrado` the "Barómetro Mensual - 2000-2018 all data" file from http://analisis.cis.es/fid/fidHistorico.jsp. This requires an account. Following log-in, go to the "Ficheros Integrados de Datos"  page. Download the full data file. This will be downloaded as `FID_637_06bcee7b-ea6b-4f41-a74e-37a941519966.zip` (or similar, depending on date downloaded). Extract the data as is in the folder in which it was downloaded.

For month specific files, download from the CIS page into `data-raw/cis/monthly` into a folder with the following format: `YYYY-MM`. Extract the file .The final path of each monthly survey will resemble something like this: `'data-raw/cis/monthly/2018-10/MD3226/3226.sav'`

#### 2. Download CEO data

Download into `data-raw/ceo` the "Matriu de dades fusionada a partir de 2014 (presdencial)" file as `2014_Microdades_anonimitzades_fusio_cine_pres.rar` from http://ceo.gencat.cat/ca/barometre/matrius-fusionada-BOP/.  Extract the data as is in the folder in which it was downloaded.

#### 3. Download ICPS data

Download into `data-raw/icps` the "Sondeig d'opinió Catalunya 2018" data from https://www.icps.cat/recerca/sondeigs-i-dades/sondeigs/sondeigs-d-opinio-catalunya. This will require creating an account and password. Download both the 2017 and 2018 data into the 'data' sub-folder.

#### 4. Download sentiment data

Download the following into `data-raw/sentiment`: http://www.saifmohammad.com/WebDocs/NRC-Emotion-Lexicon-v0.92-InManyLanguages-web.xlsx
