---
title: 'Is the Catalan independence movement "populist"?'
output: github_document
bibliography: bibliography.bib
---


```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.path = 'figures/')
```


```{r}
# Libraries
library(vilaweb)
library(rtweet)
library(tidyverse)
library(databrew)
library(waffle)

# Read functions' definitions
source('functions.R')
```

# Introduction

Opponents of Catalan independence often characterize the movement as "populist". The intent of this characterization is to highlight similarities between the Catalan indpendence movement and populist movements with generally negative reputations, such as Brexit, Marine Le Pen's National French, Donald Trump's Republican party, the right-wing Spanish party Vox, etc. 

"Populist" is hard to define, and multiple definitions exist. But an overview of the academic literature regarding populism reveals three general characteristics of modern populism:

1. *Low income*: Populism receives most support from those with low incomes [@Piketty2018].  

2. *Low education*: Populism receives most support from those with low education [@Waller_2017].

3. *Xenophobia*: Populism receives most support from those who are opposed to immigration and outsiders [@Rydgren_2003].

4. *Unhappiness*: Populism receives most support from those who are discontent, not only with politics, but with life/society in general [@Spruyt_2016].

Here is some text .