---
title: "Migration"
output: github_document
---


```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 8.64,
               fig.height = 4.86,
               fig.path = 'figures/')
```


```{r}
# Libraries
library(vilaweb)
library(tidyverse)
library(ggplot2)
library(tidyr)
library(gganimate)
```

# Article

In the last 6 years, 18,000 human beings have died trying to reach Europe through the Mediterranean. Many of them were fleeing situations of poverty, violence, and terror. They came seeking better lives for themselves and their children. Many of them were children.

They crossed countries, sometimes continents, with nothing but a bag on their back, or an infant in their arms. They died in the same waters we go to on vacation, sometimes within sight of the beach. Most drowned. Some were crushed or suffocated in a panic as their boats took on water. Some died of hypothermia, as they treaded water for hours, waiting for a rescue operation which never came. Others were lost at sea, eventually succumbing to dehydration or starvation after days adrift. 

Much of data analysis is about _aggregation_: the act of combining things together so as to convert individual data points into a meaningful narrative. But in the case of migrant deaths in the Mediterranean, it's difficult to conclude anything meaningful from something so unnecessary and meaningless. It's difficult, with or without data, to make sense of a world where tens of thousands of deaths can be considered "legal", [but rescuing people at sea is treated as a "crime"](https://www.vilaweb.cat/noticies/calvo-recorda-a-lopen-arms-que-no-te-permis-per-fer-rescats-i-que-sarrisca-a-sancions/). Furthermore, data aggregation runs the risk of converting human beings into simple numbers, losing the emotional effect which the death of a fellow person _should_ have on us.

So, this week's "analysis" won't be an analysis at all. Rather, I'll present just one data visualization: a map. The map has no aggregation, no words, and no interpretation. Rather, there's a dot for each person who has died trying to reach Europe through the Mediterranean since 2014. The map is [HERE](http://joebrew.net/mapa.html).

17.755 dots. 17.755 humans. 17.755 deaths.

Sometimes there are no words. A vegades, sobren les paraules.

# Details
- Raw data from https://missingmigrants.iom.int/
- Points randomly "jittered" within 0.08 lat/lng in order to avoid overlap
- All code at `r self_cite()` 
- Map at http://joebrew.net/mapa.html

# Instruccions per Vilaweb

- Descarrega el fitxer `.html` del mapa a https://github.com/joebrew/vilaweb/blob/master/analyses/migracio/map.html?raw=true per poder posar en el domini www.vilaweb.cat

- Si ho vols integrat en una altre pàgina, feu servir iframe així:

```
<!DOCTYPE html PUBLIC "-//W3C//DTD XHTML 1.0 Transitional//EN" "http://www.w3.org/TR/xhtml1/DTD/xhtml1-transitional.dtd">
<html xmlns="http://www.w3.org/1999/xhtml">
    <head>
        <title>Morts al mediterrànea, 2014-2019</title>
        <style type="text/css">
            body, html
            {
                margin: 0; padding: 0; height: 100%; overflow: hidden;
            }

            #content
            {
                position:absolute; left: 0; right: 0; bottom: 0; top: 0px;
            }
        </style>
    </head>
    <body>
        <div id="content">
            <iframe width="100%" height="100%" frameborder="0" src="http://joebrew.net/mapa" frameborder="0" width="960" />
        </div>
    </body>
</html>

```



