---
title: "Cotxes"
output:
  github_document:
    toc: true
    toc_depth: 2
---


```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.height = 8,
               fig.path = 'cotxes_figures/')
```


```{r}
# Libraries
library(vilaweb)
library(rtweet)
library(tidyverse)
library(databrew)
library(translateR)
library(sentimentr) # https://github.com/trinker/sentimentr
require(RPostgreSQL)
require(readr)  
require(DBI)
library(webshot)
```

```{r}
# #Coches dañados
# system("python3 ../../foreign/twint/Twint.py -s 'coches dañados' --since 2017-09-15 --until 2017-09-25 -o cotxes/coches_danados.csv --csv")
# # Cotxes danyats
# system("python3 ../../foreign/twint/Twint.py -s 'cotxes danyats' --since 2017-09-15 --until 2017-09-25 -o cotxes/cotxes_danyats.csv --csv")
# #Coches destruidos
# system("python3 ../../foreign/twint/Twint.py -s 'coches destruidos' --since 2017-09-15 --until 2017-09-25 -o cotxes/coches_destruidos.csv --csv")
# # Cotxes destruits
# system("python3 ../../foreign/twint/Twint.py -s 'cotxes destruïts' --since 2017-09-15 --until 2017-09-25 -o cotxes/cotxes_destruits.csv --csv")
# # Vehículos dañados
# system("python3 ../../foreign/twint/Twint.py -s 'vehículos dañados' --since 2017-09-15 --until 2017-09-25 -o cotxes/vehiculos_danados.csv --csv")
# # vehicles danyats
# system("python3 ../../foreign/twint/Twint.py -s 'vehicles danyats' --since 2017-09-15 --until 2017-09-25 -o cotxes/vehicles_danyats.csv --csv")
# # destrozar coches
# system("python3 ../../foreign/twint/Twint.py -s 'destrozar coches' --since 2017-09-15 --until 2017-09-25 -o cotxes/destrozar_coches.csv --csv")
# # destrossar cotxes
# system("python3 ../../foreign/twint/Twint.py -s 'destrossar cotxes' --since 2017-09-15 --until 2017-09-25 -o cotxes/destrossar_cotxes --csv")
# 
# system("python3 ../../foreign/twint/Twint.py -s '\"coches\" AND \"guardia civil\"' --since 2017-09-15 --until 2017-09-25 -o cotxes/x.csv --csv")

# system("python3 ../../foreign/twint/Twint.py -s '(\"coches\" OR \"cotxes\") AND (\"guardia civil\" OR \"dañados\" OR \"danyats\" OR \"destruidos\" OR \"destruïts\" OR \"dañar\" OR \"danyar\" OR \"destrossar\" OR \"destrozar\")' --since 2017-09-15 --until 2017-09-30 -o cotxes/final.csv --csv")


cotxes_dir <- dir('cotxes', recursive = TRUE)
out_list <- list()
for(i in which(cotxes_dir == 'final/tweets.csv')){
# for(i in 1:length(cotxes_dir)){
  file_path <- paste0('cotxes/', cotxes_dir[i])
  search_string <- unlist(strsplit(file_path, '/'))[1]
  data <- read_csv(file_path) %>%
    mutate(search_string = search_string)
  out_list[[i]] <- data
}


df <- bind_rows(out_list)
df <- df %>% filter(!duplicated(id))

# Adjust for time zone
library(lubridate)
df$date_time <- as.POSIXct(paste0(df$date, ' ', df$time, ' ', '+0', df$timezone))
Sys.setenv(TZ='CET')


# df$date_time <- with_tz(df$date_time, 'CET')


agg <- df %>%
  mutate(hour = as.POSIXct(cut(date_time, 'hour'))) %>%
  group_by(hour) %>% 
  summarise(n = n(),
            retweets = sum(retweets_count, na.rm = TRUE) + 1,
            likes = sum(likes_count))
left <- data.frame(hour  = seq(min(agg$hour),
                               max(agg$hour),
                               by = 'hour'))
agg <- left_join(left, agg)
agg$n[is.na(agg$n)] <- 0
agg$retweets[is.na(agg$retweets)] <- 0
agg$likes[is.na(agg$likes)] <- 0
agg$interactions <- agg$n + agg$retweets + agg$likes

agg <- agg %>%
  filter(hour >= '2017-09-19',
         hour <= '2017-09-24')

date_breaks <- data.frame(date_time = sort(unique(agg$hour)))
date_breaks$date <- as.Date(date_breaks$date_time)
date_breaks$hour <- as.numeric(substr(date_breaks$date_time, 12, 13))
keep_breaks <- date_breaks %>%
  filter(hour %in% seq(0, 24, 4)) %>%
  dplyr::select(date_time) %>%
  .$date_time
strong_lines <- date_breaks %>%
  filter(hour %in% 0) %>%
  dplyr::select(date_time) %>%
  .$date_time

shader <- date_breaks %>% filter(hour == 0)
shader$end <- shader$date_time + hours(24)
```

# Unique tweets

```{r}
ggplot(data = agg,
       aes(x = hour,
           y = n)) +
  geom_vline(xintercept = strong_lines,
             alpha = 0.7, 
             lty = 2) +

  geom_line() +
  theme_databrew() +
  scale_x_datetime(breaks = keep_breaks) +
  # scale_x_datetime(breaks = sort(unique(agg$hour))) +
  theme(axis.text.x = element_text(angle = 90,
                                   size = 10,
                                   vjust = 0.5),
        plot.title = element_text(size = 30),
        plot.subtitle = element_text(size = 25)) +
  labs(title = 'Hourly tweets',
       x = 'Hour', y = 'Tweets',
       subtitle = 'Unique tweets only',
       caption = paste0('Search string:\n', 
                        "(\"coches\" OR \"cotxes\") AND (\"guardia civil\" OR \"dañados\" OR \"danyats\" OR \"destruidos\" OR\n\"destruïts\" OR \"dañar\" OR \"danyar\" OR \"destrossar\" OR \"destrozar\")"))

```

# Zoom-in of the above

```{r}
ggplot(data = agg %>%
         filter(hour >= '2017-09-20',
                hour <= '2017-09-22'),
       aes(x = hour,
           y = n)) +
    geom_vline(xintercept = strong_lines,
             alpha = 0.7, 
             lty = 2) +

  geom_point() +
  
  geom_line() +
  theme_databrew() +
  scale_x_datetime(breaks = keep_breaks) +
  # scale_x_datetime(breaks = sort(unique(agg$hour))) +
  theme(axis.text.x = element_text(angle = 90,
                                   size = 15,
                                   vjust = 0.5),
        plot.title = element_text(size = 30),
        plot.subtitle = element_text(size = 25)) +
  labs(title = 'Hourly tweets',
       x = 'Hour', y = 'Tweets',
       subtitle = 'Unique tweets only',
       caption = paste0('Search string:\n', 
                        "(\"coches\" OR \"cotxes\") AND (\"guardia civil\" OR \"dañados\" OR \"danyats\" OR \"destruidos\" OR\n\"destruïts\" OR \"dañar\" OR \"danyar\" OR \"destrossar\" OR \"destrozar\")"))

```


# Same as above but including retweets

```{r}
ggplot(data = agg %>%
         filter(hour >= '2017-09-20',
                hour <= '2017-09-22'),
       aes(x = hour,
           y = retweets)) +
    geom_vline(xintercept = strong_lines,
             alpha = 0.7, 
             lty = 2) +

  geom_point() +
  geom_line() +
  theme_databrew() +
  scale_x_datetime(breaks = keep_breaks) +
  # scale_x_datetime(breaks = sort(unique(agg$hour))) +
  theme(axis.text.x = element_text(angle = 90,
                                   size = 15,
                                   vjust = 0.5),
        plot.title = element_text(size = 30),
        plot.subtitle = element_text(size = 25)) +
  labs(title = 'Hourly tweets',
       x = 'Hour', y = 'Tweets',
       subtitle = 'Including retweets',
       caption = paste0('Search string:\n', 
                        "(\"coches\" OR \"cotxes\") AND (\"guardia civil\" OR \"dañados\" OR \"danyats\" OR \"destruidos\" OR\n\"destruïts\" OR \"dañar\" OR \"danyar\" OR \"destrossar\" OR \"destrozar\")"))

```


# Same as above but including all interactions (tweet + number of retweets + number of likes)

```{r}
ggplot(data = agg %>%
         filter(hour >= '2017-09-20',
                hour <= '2017-09-22'),
       aes(x = hour,
           y = interactions)) +
    geom_vline(xintercept = strong_lines,
             alpha = 0.7, 
             lty = 2) +

  geom_point() +
  geom_line() +
  theme_databrew() +
  scale_x_datetime(breaks = keep_breaks) +
  # scale_x_datetime(breaks = sort(unique(agg$hour))) +
  theme(axis.text.x = element_text(angle = 90,
                                   size = 15,
                                   vjust = 0.5),
        plot.title = element_text(size = 30),
        plot.subtitle = element_text(size = 25)) +
  labs(title = 'Hourly tweets',
       x = 'Hour', y = 'Tweets',
       subtitle = 'All interactions',
       caption = paste0('Search string:\n', 
                        "(\"coches\" OR \"cotxes\") AND (\"guardia civil\" OR \"dañados\" OR \"danyats\" OR \"destruidos\" OR\n\"destruïts\" OR \"dañar\" OR \"danyar\" OR \"destrossar\" OR \"destrozar\")"))

```

# Technical details

- Data scraped from twtiter on February 21, 2019 using the python twint library.   
- Data processed, aggregated, and visualized using R.  
- The number of retweets and likes are as of date of data retrieval  
- All code for this analysis at https://github.com/joebrew/vilaweb/tree/master/analyses/sep20/cotxes.Rmd