---
title: "Jordi Cuixart"
output:
  github_document:
    toc: true
    toc_depth: 2
---


```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.path = 'figures/')
```


```{r}
# Libraries
library(vilaweb)
library(rtweet)
library(tidyverse)
library(databrew)
library(translateR)
library(sentimentr) # https://github.com/trinker/sentimentr
require(RPostgreSQL)
require(readr)  
require(DBI)
library(webshot)
source('prepare_data.R')
# Utility for screenshotting tweets:
# https://github.com/lukehorvat/screenshot-tweet
```

# Summary

## The question 

Did Jordi Cuixart organize a "public and violent uprising" against the Spanish State ("alzarse pública y violentamente")? 

## The hypothesis

If Jordi Cuixart committed a public and violent uprising, we expect the following three conditions to be true:

1. Social media chatter about violence and Jordi Cuixart, particularly from the ideological adversaries of Cuixart (politicians opposed to Catalan independence) will be highest in the immediate aftermath of the violence.

2. Given the severity of the events, wikipedia and search engine data about Cuixart will be highest in the immediate aftermath of the violence.

3. Newspaper coverage about Cuixart will be hightest in the immediate aftermath of the violence.

## The results  

1. Hypothesis 1: REJECTED. Social media chatter about violence and Cuixart does not peak immediately after the supposed violent uprising, but rather after the entry into prison.

2. Hypothesis 2: REJECTED. Wikipedia and search engine data about Cuixart does not peak immediately after the supposed violent uprising, but rather after the entry into prison.

3. Hypothesis 3: REJECTED. Newspaper coverage about Cuixart does not peak immediately after the supposed violent uprising, but rather after the entry into prison.

## Conclusion

A public and violent uprising, were it to have taken place, would be a major, attention-worthy event. In the case of Jordi Cuixart, however, attention from social media, wikipedia, search engines, and the media did not follow the pattern of normal violent events. 

Rather, online attention to Cuixart peaked with the Judiciary's decision to imprison him. In other words, *imprisoning Cuixart was considered more attention-worthy than his supposed crime.* 

The data regarding the events of September/October 2017 are not consistent with a violent crime. The fact that Mr. Cuixart's imprisonment garnered more attention than his supposed actions are also not suggestive of a violent crime.


# Analysis

## Finding 1

```{r}
n_people <- length(unique(people_tweets$username))
n_tweets <- nrow(people_tweets)
```

_Social media chatter about violence and Jordi Cuixart, even when limited to the ideological adversaries of Cuixart (politicians opposed to Catalan independence) does not peak in the immediate days following the supposed crime._

We harvested tweets from `r n_people` well-known Spanish/Catalan politicians and political parties/groups during the supposed violent uprising organized by Cuixart (September 20th, 2017), as well as the following 2 days (September 21, 2017 and September 22nd, 2017). The list of the `r n_people` politicians was intentionally made up of politicians who are known to be against the independence of Catalonia. The `r n_people` are listed below:

```{r}
cat(paste0(sort(unique(people_tweets$username)), collapse = '\n'))
```

During the 3 days analyzed, the `r n_people` accounts generated `r n_tweets` tweets.

```{r, results = 'asis'}

pd <- people_tweets %>%
  mutate(is_cuixart = grepl('cuixart', tolower(tweet)),
         is_jordis = grepl('jordis', tolower(tweet)) &
           !grepl('jordisa', tolower(tweet)),
         is_omnium = grepl('omnium', tolower(tweet)),
         is_violence = detect_violence(tolower(tweet)),
         is_rebelion = grepl('rebel', tolower(tweet)),
         is_sedition = grepl('sedici', tolower(tweet)))

show_screenshots <- function(the_ids,
                             the_data = picture_df){
  out <- 
    the_data %>%
    filter(id %in% the_ids)
  if(nrow(out) > 0){
    for(i in 1:nrow(out)){
      cat(paste0('\n*', as.character(out$the_dates[i]), ' ', as.character(out$the_times[i]), ' ', as.character(out$the_timezones[i]), '*\n'))
      cat(paste0('\n![screenshots/', out$file[i],'](screenshots/', out$file[i], ')\n'))
    }
  }
}
```

Of these `r n_tweets` tweets:  

- `r length(which(pd$is_cuixart))` mentioned the name of Cuixart. 

```{r, results = 'asis'}
show_screenshots(the_ids = pd$id[pd$is_cuixart])
```

- `r length(which(pd$is_jordis))` mentioned the "Jordis".

```{r, results = 'asis'}
show_screenshots(the_ids = pd$id[pd$is_jordis])
```

- `r length(which(pd$is_omnium))` mentioned "Omnium".

```{r, results = 'asis'}
show_screenshots(the_ids = pd$id[pd$is_omnium])
```

- `r length(which(pd$is_violence))` mentioned "violence", "violent", etc.

```{r, results = 'asis'}
show_screenshots(the_ids = pd$id[pd$is_violence])
```

- `r length(which(pd$is_rebelion))` mentioned "rebellion", "rebel", etc.

```{r, results = 'asis'}
show_screenshots(the_ids = pd$id[pd$is_rebelion])
```

- `r length(which(pd$is_sedition))` mentioned "sedition".

```{r, results = 'asis'}
show_screenshots(the_ids = pd$id[pd$is_sedition])
```

### Comparison with actual violent events

#### The "public and violent uprising"

```{r}
plot_data <- people_tweets_long %>%
  mutate(is_violence = detect_violence(tolower(tweet))) %>%
  filter(is_violence) %>%
  group_by(date, username) %>%
  tally
left <- expand.grid(date = seq(min(plot_data$date),
                              max(plot_data$date),
                              by = 1),
                   username = sort(unique(plot_data$username)))
plot_data <- left_join(left, plot_data)
plot_data <- plot_data %>% filter(date >= '2017-09-10',
                    date <=' 2017-10-20')
ggplot(data = plot_data,
       aes(x = date,
           y = n,
           fill = username)) +
  geom_bar(stat = 'identity',alpha = 0.9) +
    # geom_smooth(se = FALSE) +
  theme_databrew() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_date(breaks = unique(plot_data$date)) +
  labs(x = 'Date',
       y = 'Tweets',
       title = 'Tweets by Spanish politicians with violence-related words',
       subtitle = 'Words: "Violence, violent". Red line at date of supposed violence.') +
  scale_fill_manual(name = '',
                    values = databrew::make_colors(n = length(unique(plot_data$username)))) +
  geom_vline(xintercept = as.Date('2017-09-20'),
             color = 'red',
             alpha = 0.7,
             lty = 2)
```


#### Violent protests in United States - August 2017 

In August 2017, violent protests took place in Charlottesville, South Carolina (USA). White supremacists marched, and many counter-protestors also convened. There were violent clashes between the two groups and on August 12th a man drove his car into a crowd, killing one person.

```{r}
pd <- usa %>%
  mutate(is_violence = grepl('violen', tolower(tweet))) %>%
  filter(is_violence) %>%
  # Adjust for time zone
  mutate(date = as.numeric(date)) %>%
  mutate(date = ifelse(as.numeric(substr(time, 1, 2)) <6,
                       date - 1,
                       date)) %>%
  mutate(date = as.Date(date, origin ='1970-01-01')) %>%
  group_by(date,username) %>%
  tally
left <- expand.grid(date = seq(min(pd$date),
                              max(pd$date),
                              by = 1),
                   username = sort(unique(pd$username)))
pd <- left_join(left, pd)
pd <- pd %>% filter(date >= '2017-08-01',
                    date <=' 2017-08-30')
ggplot(data = pd,
       aes(x = date,
           y = n,
           fill = username)) +
  geom_bar(stat = 'identity',alpha = 0.9) +
  # geom_smooth(se = FALSE) +
  theme_databrew() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_date(breaks = unique(pd$date)) +
  labs(x = 'Date',
       y = 'Views',
       title = 'Tweets by US Congressmen with violence-related words',
       subtitle = 'Words: "Violence, violent". Red line at August 12.') +
  scale_fill_manual(name = '',
                    values = databrew::make_colors(n = length(unique(pd$username)))) +
  geom_vline(xintercept = as.Date('2017-08-12'),
             color = 'red',
             alpha = 0.7,
             lty = 2)

```

## Finding 2

_Wikipedia and search engine data about Cuixart does not peak immediately after the supposed violent uprising, but rather after the entry into prison._

#### Wikipedia page views after the "uprising"


```{r}
wiki <- pv %>%
  filter(person %in% c('Jordi Cuixart', 'Jordi Sànchez')) %>%
  filter(date >= '2017-09-15',
         date <= '2017-10-20')

pd <- wiki %>%
    group_by(date,person) %>%
  summarise(n = sum(views, na.rm = TRUE))
left <- data_frame(date = seq(min(pd$date),
                              max(pd$date),
                              by = 1))
pd <- left_join(left, pd)

ggplot(data = pd,
       aes(x = date,
           y = n,
           group = person)) +
  geom_bar(stat = 'identity',alpha = 0.6) +
  # geom_smooth(se = FALSE) +
  theme_databrew() +
  theme(axis.text.x = element_text(angle = 90),
        plot.title = element_text(size = 16)) +
  scale_x_date(breaks = unique(pd$date)) +
  labs(x = 'Date',
       y = 'Views',
       title = 'Wikipedia page-views for Jordi Cuixart and Jordi Sànchez',
       subtitle = 'Spanish, Catalan, and English languages. Red line at date of supposed violence.') +
  facet_wrap(~person, scales = 'free_y',
             ncol = 1) +
  geom_vline(xintercept = as.Date('2017-09-20'),
             color = 'red',
             alpha = 0.7,
             lty = 2)
```

#### Wikipedia page views after a truly violent event

```{r}
wiki <- pv_char %>%
  # filter(person == 'Jordi Cuixart') %>%
  filter(date >= '2017-08-01',
         date <= '2017-08-31')

pd <- wiki %>%
    group_by(date,person) %>%
  summarise(n = sum(views, na.rm = TRUE))
left <- data_frame(date = seq(min(pd$date),
                              max(pd$date),
                              by = 1))
pd <- left_join(left, pd)

ggplot(data = pd,
       aes(x = date,
           y = n)) +
  geom_bar(stat = 'identity',alpha = 0.6) +
  # geom_smooth(se = FALSE) +
  theme_databrew() +
  theme(axis.text.x = element_text(angle = 90),
        plot.title = element_text(size = 15)) +
  scale_x_date(breaks = unique(pd$date)) +
  labs(x = 'Date',
       y = 'Tweets',
       title = 'Wikipedia page-views for Jason Kessler and Richard Spencer',
       subtitle = 'English language. Red line at date of violence.') +
  facet_wrap(~person,
             scales = 'free_y',
             ncol = 1) +
  geom_vline(xintercept = as.Date('2017-08-12'),
             color = 'red',
             alpha = 0.7,
             lty = 2)
```

#### Google search trends

```{r}
google_chart <- function(person = 'Jordi Cuixart',
                         dates = c('2017-07-01', '2017-12-30'),
                         red = NULL){
  pd <- gt %>%
    filter(keyword == person) %>%
    filter(date >= dates[1],
           date <= dates[2])
  g <- ggplot(data = pd,
         aes(x = date,
             y = hits)) +
    # geom_line() +
    geom_bar(stat = 'identity') +
    theme_databrew() +
    labs(x = 'Week ending on',
         y = 'Relative search load (%)',
         title = paste0('Google search trends for ', person)) +
    scale_x_date(breaks = unique(pd$date)) +
    theme(axis.text.x = element_text(angle = 90))
  if(!is.null(red)){
    g <- g + 
      geom_vline(xintercept = as.Date(red),
             color = 'red',
             alpha = 0.7,
             lty = 2)
  }
  return(g)
}

google_chart('Jordi Cuixart', red = '2017-09-23')
```

```{r}
google_chart('Jordi Sànchez', red = '2017-09-23')
```

#### Google search trends after a truly violent event


```{r}
google_chart('Jason Kessler',
             dates = as.Date(c('2017-07-01',
                               '2017-09-30')), red = '2017-08-12')
```

```{r}
google_chart('Richard Spencer',
             dates = as.Date(c('2017-07-01',
                               '2017-09-30')), red = '2017-08-12')
```

## Finding 3

_Newspaper coverage about Cuixart does not peak immediately after the supposed violent uprising, but rather after the entry into prison._


```{r}
n_papers <- length(newspapers)
n_international <- length(tolower(news$user_name))
```

We harvested tweets and headlines for `r n_papers` Spanish newspapers. We intentionally restricted our analysis only to those newspapers which a known anti-independence editorial position, so as to increase the likelihood of finding a "signal" in the "noise". The newspapers are listed below:

```{r}
cat(paste0(sort(unique(newspaper_tweets$username)), collapse = '\n'))
```

As a comparison, we also harvested tweets for `r n_international` international newspapers.

The below chart shows the use of the words "violent" and "violence" in tweets from the Spanish newspapers. The vertical red line shows the date of the supposed violent uprising organized by Jordi Cuixart and Jordi Sànchez.

```{r}
plot_data <- newspaper_tweets %>%
  mutate(is_violence = detect_violence(tolower(tweet))) %>%
  # filter(is_violence) %>%
 group_by(date,username) %>%
  summarise(n = length(which(is_violence)),
            denom = n())
left <- expand.grid(date = seq(min(plot_data$date),
                              max(plot_data$date),
                              by = 1),
                   username = sort(unique(plot_data$username)))
plot_data <- left_join(left, plot_data)
plot_data <- plot_data %>% filter(date >= '2017-09-10',
                    date <=' 2017-10-20')
plot_data$n <- ifelse(is.na(plot_data$n), 0, plot_data$n)
ggplot(data = plot_data,
       aes(x = date,
           y = n,
           fill = username)) +
  geom_bar(stat = 'identity',alpha = 0.9) +
    # geom_smooth(se = FALSE) +
  theme_databrew() +
  theme(axis.text.x = element_text(angle = 90),
        plot.title = element_text(size = 15)) +
  scale_x_date(breaks = unique(plot_data$date)) +
  labs(x = 'Date',
       y = 'Tweets',
       title = 'Tweets by Spanish newspapers with violence-related words',
       subtitle = 'Words: "Violence, violent". Red line = 20 September 2018') +
  scale_fill_manual(name = '',
                    values = databrew::make_colors(n = length(unique(plot_data$username)))) +
   geom_vline(xintercept = as.Date('2017-09-20'),
             color = 'red',
             alpha = 0.7,
             lty = 2)
```

The below shows the same time period, but for international news sources.

```{r}
plot_data <- tl %>%
  filter(date >= '2017-09-10',
         date <= '2017-10-20') %>%
  filter(username %in% tolower(news$user_name)) %>%
  mutate(is_violence = detect_violence(tolower(tweet))) %>%
  # filter(is_violence) %>%
 group_by(date,username) %>%
  summarise(n = length(which(is_violence)),
            denom = n())
left <- expand.grid(date = seq(min(plot_data$date),
                              max(plot_data$date),
                              by = 1),
                   username = sort(unique(plot_data$username)))
plot_data <- left_join(left, plot_data)

plot_data$n <- ifelse(is.na(plot_data$n), 0, plot_data$n)
ggplot(data = plot_data,
       aes(x = date,
           y = n,
           fill = username)) +
  geom_bar(stat = 'identity',alpha = 0.9) +
    # geom_smooth(se = FALSE) +
  theme_databrew() +
  theme(axis.text.x = element_text(angle = 90),
        plot.title = element_text(size = 15)) +
  scale_x_date(breaks = unique(plot_data$date)) +
  labs(x = 'Date',
       y = 'Tweets',
       title = 'Tweets by international newspapers with violence-related words',
       subtitle = 'Words: "Violence, violent". Red line = 24 July 2018') +
  scale_fill_manual(name = '',
                    values = databrew::make_colors(n = length(unique(plot_data$username)))) +
   geom_vline(xintercept = as.Date('2018-07-24'),
             color = 'red',
             alpha = 0.7,
             lty = 2) +
  geom_vline(xintercept = as.Date('2017-09-20'),
             color = 'red',
             alpha = 0.7,
             lty = 2)
```

The below shows the Spanish newspapers' frequency of tweets with violence-related words during the July 2018 Barcelona taxi strike.

```{r}
plot_data <- tl%>%
  filter(username %in% newspapers) %>%
  mutate(is_violence = detect_violence(tolower(tweet))) %>%
  # filter(is_violence) %>%
 group_by(date,username) %>%
  summarise(n = length(which(is_violence)),
            denom = n())
left <- expand.grid(date = seq(min(plot_data$date),
                              max(plot_data$date),
                              by = 1),
                   username = sort(unique(plot_data$username)))
plot_data <- left_join(left, plot_data)
plot_data <- plot_data %>% filter(date >= '2018-07-13',
                    date <=' 2018-08-08')
plot_data$n <- ifelse(is.na(plot_data$n), 0, plot_data$n)
ggplot(data = plot_data,
       aes(x = date,
           y = n,
           fill = username)) +
  geom_bar(stat = 'identity',alpha = 0.9) +
    # geom_smooth(se = FALSE) +
  theme_databrew() +
  theme(axis.text.x = element_text(angle = 90),
        plot.title = element_text(size = 15)) +
  scale_x_date(breaks = unique(plot_data$date)) +
  labs(x = 'Date',
       y = 'Tweets',
       title = 'Tweets by international newspapers with violence-related words',
       subtitle = 'Words: "Violence, violent". Red line = 24 July 2018') +
  scale_fill_manual(name = '',
                    values = databrew::make_colors(n = length(unique(plot_data$username)))) +
   geom_vline(xintercept = as.Date('2018-07-24'),
             color = 'red',
             alpha = 0.7,
             lty = 2)
```


The below shows the international newspapers' frequency of tweets with violence-related words during the July 2018 Barcelona taxi strike.

```{r}
plot_data <- tl%>%
  filter(username %in% tolower(news$user_name)) %>%
  mutate(is_violence = detect_violence(tolower(tweet))) %>%
  # filter(is_violence) %>%
 group_by(date,username) %>%
  summarise(n = length(which(is_violence)),
            denom = n())
left <- expand.grid(date = seq(min(plot_data$date),
                              max(plot_data$date),
                              by = 1),
                   username = sort(unique(plot_data$username)))
plot_data <- left_join(left, plot_data)
plot_data <- plot_data %>% filter(date >= '2018-07-13',
                    date <=' 2018-08-08')
plot_data$n <- ifelse(is.na(plot_data$n), 0, plot_data$n)
ggplot(data = plot_data,
       aes(x = date,
           y = n,
           fill = username)) +
  geom_bar(stat = 'identity',alpha = 0.9) +
    # geom_smooth(se = FALSE) +
  theme_databrew() +
  theme(axis.text.x = element_text(angle = 90),
        plot.title = element_text(size = 15)) +
  scale_x_date(breaks = unique(plot_data$date)) +
  labs(x = 'Date',
       y = 'Tweets',
       title = 'Tweets by international newspapers with violence-related words',
       subtitle = 'Words: "Violence, violent". Red line = 24 July 2018') +
  scale_fill_manual(name = '',
                    values = databrew::make_colors(n = length(unique(plot_data$username)))) +
   geom_vline(xintercept = as.Date('2018-07-24'),
             color = 'red',
             alpha = 0.7,
             lty = 2)
```


```{r}
n_t <- plot_data %>% group_by(date) %>% summarise(n = sum(n)) %>% filter(date >= '2017-09-20', date <= '2017-09-22') %>% summarise(x = sum(n)) %>% .$x

# taxis
n_tt <- plot_data %>% group_by(date) %>% summarise(n = sum(n)) %>% filter(date >= '2018-07-24', date <= '2018-07-26') %>% summarise(x = sum(n)) %>% .$x
```

During the three day period from September 20-22 2017, the period during and immediately after the violent public uprising, these 8 newspapers issued only a total of `r n_t` tweets with the words "violent" or "violence".

On the other hand, during the three day period from July 24-July 26, 2018, the period of the Barcelona taxi drivers protest, these 8 newspapers issued `r n_tt` tweets with the words "violent" or "violence".

#### Actual violent event: 2016 Turkish coup

The below shows international news coverage of the Turkish coup attempt in July 2016.


```{r}
plot_data <- turkey %>%
  filter(is_international) %>%
  mutate(is_violence = detect_violence(tolower(tweet))) %>%
  # filter(is_violence) %>%
 group_by(date,username) %>%
  summarise(n = length(which(is_violence)),
            denom = n())
left <- expand.grid(date = seq(min(plot_data$date),
                              max(plot_data$date),
                              by = 1),
                   username = sort(unique(plot_data$username)))
plot_data <- left_join(left, plot_data)

plot_data$n <- ifelse(is.na(plot_data$n), 0, plot_data$n)
ggplot(data = plot_data,
       aes(x = date,
           y = n,
           fill = username)) +
  geom_bar(stat = 'identity',alpha = 0.9) +
    # geom_smooth(se = FALSE) +
  theme_databrew() +
  theme(axis.text.x = element_text(angle = 90),
        plot.title = element_text(size = 15)) +
  scale_x_date(breaks = unique(plot_data$date)) +
  labs(x = 'Date',
       y = 'Tweets',
       title = 'Tweets by international newspapers with violence-related words',
       subtitle = 'Words: "Violence, violent". Red line = 24 July 2018') +
  scale_fill_manual(name = '',
                    values = databrew::make_colors(n = length(unique(plot_data$username)))) +
   geom_vline(xintercept = as.Date('2018-07-24'),
             color = 'red',
             alpha = 0.7,
             lty = 2)
```


#### Tweets about Cuixart

As the organizer of a public, violent uprising, we would expect a great deal of media coverage to mention the perpetrator of the crime in the immediate days following the crime. However, this is not the case.

```{r}
plot_data <- newspaper_tweets %>%
  mutate(is_cuixart = grepl('cuixart', tolower(tweet))) %>%
  filter(is_cuixart) %>%
  group_by(date,username) %>%
  tally
left <- expand.grid(date = seq(min(newspaper_tweets$date),
                              max(newspaper_tweets$date),
                              by = 1),
                   username = sort(unique(plot_data$username)))
plot_data <- left_join(left, plot_data)
plot_data <- plot_data %>% filter(date >= '2017-09-10',
                    date <=' 2017-10-20')
plot_data$n <- ifelse(is.na(plot_data$n), 0, plot_data$n)
ggplot(data = plot_data,
       aes(x = date,
           y = n,
           fill = username)) +
  geom_bar(stat = 'identity',alpha = 0.9) +
    # geom_smooth(se = FALSE) +
  theme_databrew() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_date(breaks = unique(plot_data$date)) +
  labs(x = 'Date',
       y = 'Tweets',
       title = 'Tweets by Spanish newspapers about Cuixart',
       subtitle = 'Red line: 20 September 2018') +
  scale_fill_manual(name = '',
                    values = databrew::make_colors(n = length(unique(plot_data$username)))) +
     geom_vline(xintercept = as.Date('2017-09-20'),
             color = 'red',
             alpha = 0.7,
             lty = 2)
```

#### Newspaper headlines

If a public, violent uprising occurred on the night between September 20th and 21st, we would expect that newspaper headlines would discuss this transcendentally important event. Let's examine those headlines.

What follows are headlines for major newspapers on the dates of September 21 and 22. Coverage focused on police operations. There were some mentions of the "protests", but in no case was violence mentioned. The only use of violence-related words in reference to the protests (El Mundo, September 22) is actually a quote of the judiciary: "ataques y presiones", and not an observation of any journalist. In other instances (La Razón, September 22; El Mundo, September 22), the worst language to describe the protestors behavior was "acoso" (harassment).  In no cases is violence mentioned.



```{r, echo = F, results = 'asis'}
newspaper_df <- 
  data_frame(file = dir('newspaper_headlines')) %>%
  mutate(paper = unlist(lapply(lapply(strsplit(file, '_'), function(x){x[2]}), function(y){gsub('.jpg', '', y, fixed = T)}))) %>%
  mutate(date = as.Date(substr(file, 1, 10))) %>%
  mutate(file = paste0('newspaper_headlines/', file))

sub_newspapers <- newspaper_df %>%
  filter((date >= '2017-09-21'&
         date <= '2017-09-22'))
sub_newspapers <- sub_newspapers %>%
  arrange(date, paper)
for(i in 1:nrow(sub_newspapers)){
   this_file <- sub_newspapers$file[i]
  new_person <- FALSE
  if(i == 1){
    new_person <- TRUE
  } else if(sub_newspapers$date[i] != sub_newspapers$date[i-1]){
    new_person <- TRUE
  }
  if(new_person){
    cat(paste0('\n### ', as.character(sub_newspapers$date[i]), '\n\n'))
  }
  cat(paste0('\n##### ', as.character(sub_newspapers$date[i]), ', ',   as.character(sub_newspapers$paper[i]), '\n'))
  cat(paste0('\n![',this_file,'](', this_file, ')\n'))
}
```


# Conclusion

Did Jordi Cuixart carry out a public and violent uprising on the night of September 20th, 2017? The data from Twitter, Google, Wikipedia, and newspapers suggest not.

Rebellion is - by definition - violent and public. Violence is attention-worthy: when it occurs, politicians (particularly those opposed to the executors of the violence) tweet about it. Violence is news-worthy: when it occurs, newspapers write about it. Violence is interest-worthy: when it occurs, people search about the culprits of the violence on google and wikipedia to learn more.

How is it, then, that Jordi Cuixart managed to carry out a violent and public uprising and almost nobody noticed? Is it reasonable that Cuixart 

# Appendix

https://github.com/joebrew/vilaweb/tree/master/analyses/sep20/appendix.md
