---
title: "Federalist fantasies: why the Catalonia-Spain territorial conflict won't likely be resolved through reform"
output: github_document
---


```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 8.64,
               fig.height = 4.86,
               fig.path = 'figures/')
```

```{r}
source('prepare_data.R')
```

# Introduction

A window of hope has been opened in recent weeks as Spain's government has agreed to enter into dialogue with Catalonia's government. This hope has been bolstered by the recent admission by Spanish President Pedro Sánchez that the crisis in Catalonia is indeed "political" (he had previously maintained that it was a "crisis of coexistence" among Catalans, not a political problem between Catalonia and Spain). Recognizing the existence of a problem's "political" nature implies recognizing that the problem's solution must also be "political" (as opposed to the "judicial" strategy used by the Spanish State to combat independentism over the last few years).

Given these conditions, an optimist might be led to believe that a political resolution to the Catalonia-Spain territorial conflict is coming soon. An optimist might think that Spain would follow the paths of Canada and the United Kingdom, offering greater decentralization and autonomy to independence-seeking regions, in order to decrease support for independence among the inhabitants of those regions. An optimist might believe that the severity of the ongoing territorial crisis in Spain will soon lead to a constitutional reform so as to create a federalist state in which a majority of Catalans are satisfied within the Spanish State.

In fact, the "federalist" solution has long been advocated for by Catalan socialists as a sort of "third way" between independence and immobility. The rationale is that "federalism" - or other forms of decentralization - could satisfy both those independentists who want more self-government as well as those unionists who want Catalonia to remain Spanish. An optimist might perceive the current political moment as the perfect time for Spain to finally roll out its inevitable federalist reform, thereby satisfying both independentists and unionists.


Unfortunately, given the underlying electoral arithmetic in Spain and Catalonia, that optimist would be wrong. Pedro Sánchez cannot "offer" federalism or decentralization as a solution to Catalans' calls for more autonomy, for the same reason he cannot "offer" permitting Catalan self-determination: a large majority of Spaniards want the opposite. In other words, the concepts of (a) granting Catalonia more autonomy or (b) making Spain less centralized are both illegal and extremely unpopular in most of Spain.

The prospect of a federalist or decentralizing reform might be politically useful to those who want to difuse the tense situation between the governments of Spain and Catalonia, but its likelihood of success is essentially zero. Proposing either (a) an explicit federalist reform for the entire State or (b) increased autonomy for Catalonia might capture the support of a majority of Catalans, but it would be politically suicidal at the level of the Spanish State.

In this article, I'll use data to make 2 simple points:

1. That there is a consensus in Catalonia in favor of more self-government and increased autonomy (including options such as independence or federalism).

2. That there is a consensus in Spain (outside of Catalonia) in favor of _reducing_ Catalonia's autonomy, and creating a more centralized state.  


The combination of these points leads to an obvious conclusion: as good as a federalist "third way" might be (for both Spain and Catalonia), it's simply not feasible. In other words, the Catalonia-Spain territorial conflict has only two _realistic_ resolutions: independence or status quo.

# 1. The Catalan consensus in favor of more Catalan self-government

In terms of the degree of self-government, a large majority of Catalans are opposed to the status quo. Fewer than one quarter (24.6%) believe that Catalonia has achieved a "sufficient" level of autonomy. Just 8.5% feel that Catalonia has _too much_ autonomy, whereas 6 times as many (62.5%) feel that Catalonia does not have eough autonomy.

```{r}
plot_self_government(ca = FALSE)
```

The Catalan consensus for decentralization is very clear; when asked about their preferences for the territorial organization of Spain, two-thirds of Catalans (66%) want Spain "autonomous communities" (regions) to have either more autonomy or the possibility of independence. Only 16% want to keep the current system of autonomous communities, and fewer than 14% want a more centralized Spain.

```{r}
plot_centralism(ca = FALSE)
```

Perhaps the most interesting data point on Catalans' views regarding territorial organization is the high prevalence of _conditional_ independentists. That is, though many Catalans want independence (49,3% in favor vs. 41,2% opposed in this particular survey), a significant percentage (16%) of those Catalans who say they are in favor of independence (when asked a yes/no question) say that they prefer being a state in a federal Spain if given the option. 

In other words, offering a "federation" to Catalonia would reduce support for indepenence to well below 50%. So, if Spain wants to "defeat" the indepenence movement, why not go with this obvious option? That brings us to point 2.


# 2. The Spanish consensus against Catalan self-government and decentralization

Outside of Catalonia, there is a large degree of consensus _against_ granting Catalonia more autonomy, or granting autonomous communities more generally any more self-government. Even a large majority of Catalans want _more_ autonomy, a majority of Spaniards (outside of Catalonia), 51.1%, think that Catalonia has _too much_ autonomy. 


```{r}
plot_self_government_es(agg = T)
```

If we break the above down by autonomous community, we see that there is mostly uniformity. Large majorities of each of Spain's autonomous communities believe that Catalonia already has _too much_ autonomy (the notable exception being the Basque country, where a majority feel the opposite).

```{r}
plot_self_government_es(ca = F)
```

Given these data, is a reform in which Catalonia is granted more autonomy feasible? Of course not. Most Spaniards feel that Catalonia has too much autonomy already; if any reform had electoral viability, it would be one in which autonomy was stripped from Catalonia (case in point: Spain's suspension of Catalan self-rule in 2017 and 2018 had large popular support in the rest of Spain, but was opposed by a majority of Catalans).

Since a "special" deal granting Catalonia more autonomy doesn't appear to be electorally possible, perhaps _all of Spain_ could undergo a reform. That way, the electorate (which is opposed to granting Catalans more autonomy) would feel that they are getting the same "privileges" as Catalans.

This, too, is electorally impossible. Unlike Catalonia, where two-thirds want a State with more autonomy, in the rest of Spain only a small minority (22%) want a state with more autonomy for its constituent parts.

```{r}
plot_centralism_es(ca = FALSE, agg = T)
```

Again, the Basque country is the exception here (a large majority of Basques, like Catalans, want a more decentralized State), but it is relatively so small in terms of population (compared to the rest of the State), that even its strong preference in favor of more autonomy makes no significant difference.

```{r}
plot_centralism_es(ca = FALSE, agg = F)
```


# Conclusion

In the case of the Catalonia-Spain territorial conflict, it's clear that both Spaniards and Catalans agree that there is a problem. But they disagree on the nature of that problem. Catalans largely want more autonomy and more decentralization; in the rest of the Spanish State (except the Basque country), they want the opposite.

Solving the Catalonia-Spain crisis through reform is, of course, a desirable outcome. The most frequently proposed reform-based solution is giving more autonomy to Catalonia, or decentralizing the Spanish State. These proposals are intelligent in the sense that their fulfillment would likely indeed reduce the support for Catalan independence to a minority. But Catalan support for a federal Spain is not sufficient to create a federal Spain; this would require Spanish support. And, frankly, this is not possible: the data on prefences regarding (a) Catalonia's autonomy and (b) the territorial organization of the Spanish state as a whole show that Spaniards would not accept a solution which granted Catalonia more autonomy or resulted in a more decentralized state. 

Despite all the talk about federalism or constitutional reform as a means to resolve the political crisis between Catalonia and Spain, it's not realistic. Either (a) the majority of Catalans in favor of self-determination and greater autonomy need to change their mind or (b) the majority of Spaniards opposed to self-determination and greater autonomy need to change their mind. Since neither is likely to happen, further political deadlock is the most probable outcome. Reform of any kind is unlikely, and the only option which is even close to reaching a significant majority capable of reform would be those in favor of centralization, not federalism.

"Federalists" often accuse Catalan "independentists" of being "unrealistic", since (legal) independence would require a constitutional reform for which there is not sufficient popular support in Spain. Ironically, the federalist proposal is, like independence, both "illegal" and lacking in popular support in Spain. But, unlike independence (for which there are many historical examples of "unilateral" success, ie, a country achieving independence without the permission from the state it leaves), there are no examples of a state achieving federalism against the wishes of its citizens. Even though a federal reform _could_ reduce support for Catalan independence (since many pro-independence Catalans would be satisfied with it), it _won't_ because the (much more numerous) Spanish population is opposed to it. In other words, Spanish federalism is of lower probability than Catalan independence.

What does the lack of decentralizing reformability mean for the future of the Spain-Catalonia conflict? Spain's coalition government will likely continue to wave the flag of dialogue, as a signal to Catalans that it wants to engage in constructive reform; however, given the majority opposition in the rest of Spain, Sánchez's government will be unable to offer anything concrete (doing so would be electoral suicide). Given the lack of a political offer, the "grace period" given to Sánchez by pro-independence Catalans will likely come to an end. That is, the window of hope that Sánchez will resolve the conflict will close when it becomes clear that the mechanism which could assuage Catalans (federalism) is not possible. And, as time passes and no federalist reform materializes, some pro-decentralization Catalans who were previously anti-independence will become disenchanted with Spain's immobility and convert to the pro-independence camp. In other words, the (inevitable) lack of a federalist solution to the Catalonia-Spain political conflict will most likely generate _more_ support among Catalans for independence from Spain.


# Catalan-language charts



```{r}
plot_self_government(ca = TRUE)
```


```{r}
plot_centralism(ca = TRUE)
```

```{r}
plot_self_government_es(ca = T, agg = T)
```

```{r}
plot_self_government_es(ca = T)
```

```{r}
plot_centralism_es(ca = TRUE, agg = T)
```

```{r}
plot_centralism_es(ca = TRUE, agg = F)
```

# Data and technical details

All of the data used in this article came from the "Percepció sobre el debat territorial a Espanya. 2019" survey carried out in Spain and Catalonia in September-October 2019. The data are openly available at the website of the Catalan [Centre d'Estudis d'Opinió](http://ceo.gencat.cat/ca/estudis/registre-estudis-dopinio/estudis-de-la-generalitat/detall/index.html?id=7368).

The code used for this analysis is also publicly available: `r self_cite()`.